VariantSpark: Population Scale Clustering of Genotype Information

### 2015-09-03 doc/publications/journal2014/paper.tex
more stuff

>>>>

\subsection*{Datasets}
We used  phase 1 variants from the 1000 Genomes Project. On the 22 autosomes, this dataset contains variants for 1092 individuals, spread over a total 38,219,238 alleles.
We use chromosome 22 for some comparisons, and this contains variants over 494,328 alleles.
These individuals from these datasets are distributed across four super populations, African (AFR), Mixed American (AMR), East Asian (EAS) and European (EUR).
